Nonparametric Spectral Siren Cosmology

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Introduction}
\label{sec:intro}
Like light, gravitational waves (GWs) are redshifted as they propagate across the universe.
Unlike light, however, the selection effects of GWs are extremely well understood, allowing for a precise estimate of each catalogs’ completeness and an unbiased measurement of the true GW population.
This allows GW signals to be used as relatively clean probes of cosmological parameters \citep[e.g.][]{bright sirens first paper, 170817 bright siren, dark siren first paper, dark siren with 0817, hithhikers guide}.

>>>>

\section{Introduction}
\label{sec:intro}
Like light, gravitational waves (GWs) are redshifted as they propagate across the universe.
Unlike light, however, the selection effects of GWs are extremely well understood, allowing for a precise estimate of each catalogs’ completeness and an unbiased measurement of the true GW population.
This allows GW signals to be used as relatively clean probes of cosmological parameters %\citep[e.g.][]{bright sirens first paper, 170817 bright siren, dark siren first paper, dark siren with 0817, hithhikers guide}.
